|

### 2022-12-30 paper.Rmd
autogit

```{bash ipythonRunner, eval=FALSE, include=FALSE}
# Set the base directory
EXPDIR="/Users/rmn/masterThesis/eda-gp-2020"

# Find all *.ipynb files in subdirectories of EXPDIR, including sub-sub directories, etc., but exclude files that contain the word "checkpoint" in the filename
for file in $(find "$EXPDIR" -type f -name "*.ipynb" ! -name "*checkpoint*"); do
  # Change to the directory containing the IPython notebook file
  cd "$(dirname "$file")"
  # Execute the IPython notebook file using the jupyter nbconvert command
  ipython "$(basename "$file")"
done

@@

![Flowchart - Regular DAE-GP](./img/flowcharts/dae-gp.png){height=900px width=200px}

@@

![Flowchart - Pre-Trained DAE-GP](./img/flowcharts/pt-dae-gp.png){height=800px width=200px}

@@

>>>>

@@

![Flowchart - Regular DAE-GP](./img/flowcharts/dae-gp.png)

@@

![Flowchart - Pre-Trained DAE-GP](./img/flowcharts/pt-dae-gp.png)

@@

```{bash compile_airfoil_2hl_maxIndSize_fullRun_30gens, include=FALSE}
bash /Users/rmn/masterThesis/eda-gp-2020/experiments/airfoil_2hl_maxIndSize_fullRun_30gens/re_evaluate_airfoil_2hl_maxIndSize_30gen.sh
```
